---
title: "Feldman"
author: "Ben Brew"
date: "July 25, 2018"
output: html_document
css: markdown_theme.css
---

```{r setup, include=FALSE}
# initialize libraries 
library(databrew)
library(flextable)
library(readr)
library(xlsx)
library(knitr)
library(kableExtra)
library(plotly)

knitr::opts_chunk$set(echo = TRUE)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
```

## This script will read in data from research by Alexandar et al and create graphics with a unique theme


```{r cars, warning=FALSE, echo=T, results='hide'}
# source functions script for custom functions and sfi themes
source('functions.R')
source('sfi_theme.R')
source('sfi_theme_stata.R')

# suppress scientific notation in plots
options(scipen=999)

```

<!-- <div class="large"> -->

## Figure 1 

Please not that the data given to us is slightly different than the data in the paper. For examle, the paper cites that there are 4,046 observations, but the data
from box only has 3,856. The minimum and maximum of the clarity scores reported in the paper are also slightly different than the data we have. The distribution of the 
clarity scores, and thus the plot, are very similar though.
```{r echo=T, results='hide'}

# create an object to store the path to the data
data_folder <- '../data/Feldman'

# read in data from Feldman folder
figure_1 <- read_csv(paste0(data_folder, '/Fig1Data_AF.csv'))

# rename columns for ease of coding
names(figure_1) <- c('federal_state', 'clarity_score')

# restructure data types for plotting
figure_1$federal_state <- as.character(figure_1$federal_state)

# add a color vector to the data frame
figure_1$colors <- ifelse(figure_1$federal_state == '0', "#D7D6D6", "#545454")

# recode federal state levels for graph
figure_1$federal_state <- ifelse(figure_1$federal_state == '1', 'Federal', 'State')

```

## Figure 1 with SFI R theme
```{r echo=T, results='hide'}
# using R theme
ggplot(figure_1, aes(x = clarity_score, fill = federal_state))  +
  geom_histogram(aes(y=..density..), bins = 75, alpha = 0.3, color = 'black') +
  labs(x = 'Clarity score', y = 'Density', title = 'Figure 1') +
    scale_fill_manual(name = '' ,
                      values = c("#ffffff", "#545454")) + theme_sfi()


```


## Figure 1 with SFI stata theme
```{r echo=T, results='hide'}
# using R theme
ggplot(figure_1, aes(x = clarity_score, fill = federal_state))  +
  geom_histogram(aes(y=..density..), bins = 75, alpha = 0.3, color = 'black') +
  labs(x = 'Clarity score', y = 'Density', title = 'Figure 1') +
    scale_fill_manual(name = '' ,
                      values = c("#ffffff", "#545454")) + theme_sfi_stata()


```


## Another version of Figure 1 using R theme (adjusting arguments in the theme function)
```{r echo=T, results='hide'}
# using R theme
ggplot(figure_1, aes(x = clarity_score, fill = federal_state))  +
  geom_histogram(aes(y=..density..), bins = 75, alpha = 0.3) +
  labs(x = 'Clarity score', y = 'Density', title = 'Figure 1') +
    scale_fill_manual(name = '' ,
                      values = c("black", "#545454")) + theme_sfi(gm = TRUE, gc = 'gray', gl = 'solid')


```


# Figure 2 Kernel density plot.

```{r echo=T, results='hide'}

# read in data from Feldman folder
figure_2 <- read_csv(paste0(data_folder, '/Fig2Data_AF.csv'))

# rename columns for ease of coding
names(figure_2) <- c('federal_state', 'words')

# restructure data types for plotting
figure_2$federal_state <- as.character(figure_2$federal_state)

# add a color vector to the data frame
figure_2$colors <- ifelse(figure_2$federal_state == '0', "#D7D6D6", "#545454")

# recode federal state levels for graph
figure_2$federal_state <- as.factor(ifelse(figure_2$federal_state == '1', 'Federal', 'State'))

# # subset figure_2 by removing all rows where words is over 20k (to mimic plot in the paper)
# figure_2 <- figure_2 %>% dplyr::filter(words <= 20000)

```


Figure 2 group by line type
```{r echo=T, results='hide'}
# estimate kernel density using word column and grouping by line type
ggplot(figure_2, aes(x = words)) +
  stat_density(aes(group = federal_state, linetype = federal_state),
               position="identity",
               geom="line", kernel = "gaussian", size = 0.5) +
  xlim(c(0, 20000)) + 
   scale_fill_manual(name = '' ,
                     values = c("black", "#545454")) +
  labs(x = 'Words', y = 'Kernel Density') +
  theme_sfi()

```


Figure 2 group by color
```{r}
# estimate kernel density using word column and grouping by color
ggplot(figure_2, aes(x = words)) +
  stat_density(aes(group = federal_state, color = federal_state),
               position="identity",
               geom="line", kernel = "gaussian", size = 1, alpha = 0.7) +
  xlim(c(0, 20000)) + 
   scale_color_manual(name = '' ,
                     values = c("black", "#D3D3D3")) +
  labs(x = 'Words', y = 'Kernel Density') +
  theme_sfi()

```